---
title: "The Impact of Thoughts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
packages.used=c("rvest", "tibble", 
                "sentimentr", "gplots", "dplyr",
                "tm", "syuzhet", "factoextra", 
                "beeswarm", "scales", "RColorBrewer",
                "RANN", "topicmodels", "stringr")
# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))
# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}
library(ggplot2)
library(dplyr)
library(redav)
library(textmineR)
```


```{r}
philosophy_data <- read.csv("../data/philosophy_data.csv")
```


## Intro

Philosophers provide a way to think about the world systematically. Some of their thoughts are coincided, some are conflicted. One question raised naturally: when they develop their works, are they inspired by other philosopher in some way? 

Can we figure out the influence of philosophers' words though history? To be specific, how philosophers influence their colleagues and the history?


To find how philosophers influence each other, I analyzed the history of philosophy dataset from [Philosophy Data Project](http://www.philosophydata.com/).



## Looking into the dataset

In order to get a better sense of what data we are analyzing, we first take a glimpse on the dataset.

### Column Details

* title
* author
* school
* sentence_spacy
* sentence_str
* original_publication_date
* corpus_edition_date
* sentence_length
* sentence_lowered
* tokenized_txt
* lemmatized_str

The dataset is pre-processed and each row contains one sentence and school, author, and other information.

### missing values

```{r, warning=FALSE}
missing_philosophy_data_show_case <- philosophy_data %>% 
  select(title, author,school, sentence_str, original_publication_date) %>%
  rename(date = original_publication_date)
plot_missing(missing_philosophy_data_show_case)
```

There is no missing values, and total contains 360808 complete sentences.

```{r}
unique(philosophy_data['school'])
unique(philosophy_data['author'])
```

Only 13 school and 36 distinct philosophers! Assumption is philosophers under same school could influence each other a lot. 

## Influence Analysis

To find influence of a philosopher, we can dive into the corpus and find connections. 

It is firstly reasonable to speculate that if one philosopher mention another philosopher directly in their own corpus, then he/she is impacted by the philosopher. At this stage we can count the author name in all texts

```{r}
philosopher = unique(philosophy_data['author'])
occurance = rep(0, nrow(philosopher))
direct_citation <- data.frame(philosopher, occurance)
for (i in 1:nrow(philosopher)) {
    # find direct citation, exclude self-cited corpus
    direct_citation[i,2] = sum(grepl(tolower(direct_citation[i,1]), (philosophy_data %>% filter(!author %in%c(direct_citation[i,1])))$sentence_lowered))
}
rownames(direct_citation) <- 1:nrow(direct_citation)
```

```{r}
p<-ggplot(data=top_n(direct_citation, 10), aes(x=reorder(author, -occurance), y=occurance)) +
  geom_bar(stat="identity") +
  xlab("philosopher") + 
  ggtitle("top 10 philosophers mentioned directly in corpus")
p
```
Here we plot top 10 philosophers' name. Intuitively, ancient philosophers should have higher chance to be cited in corpus. Surprisingly, the top 3 authors mentioned in corpus are not ancient Greek philosophers such as Plato and Aristotle. Instead, Kant, Descartes and Russell are the top 3 directed recorded philosophers in history of philosophy. We could further investigate what lead to this situation by examine the correlation between philosophers' occurrence in corpus and other potential factors such as their corpus length, time period they lived etc.

```{r}
citation_factors <- philosophy_data %>% group_by(author, school) %>% summarise(total_length = sum(sentence_length), time_period = mean(original_publication_date))
```

```{r}
citation <- merge(direct_citation, citation_factors, by.x = "author", 
             by.y = "author", all.x = TRUE, all.y = FALSE)
```



```{r}
kruskal.test(occurance ~ school, data = citation)
kruskal.test(occurance ~ time_period, data = citation)
kruskal.test(occurance ~ total_length, data = citation)
```

The three KW test suggested all have quite big p-values, which implies the reputations of philosophers are uncorrelated with their publications' length, school they are in, and the time period they lived.

We could then cluster the philosophers by schools, find their school influence by capturing occurrence of their school in philosophy corpus

```{r}
school = unique(philosophy_data['school'])
occurance = rep(0, nrow(school))
school_reputation <- data.frame(school, occurance)
for (i in 1:nrow(school)) {
    # find direct citation, exclude self-cited corpus
    school_reputation[i,2] = sum(grepl(tolower(school_reputation[i,1]), (philosophy_data %>% filter(!school %in%c(school_reputation[i,1])))$sentence_lowered))
}
```

```{r}
p2<-ggplot(data=school_reputation, aes(x=reorder(school, -occurance), y=occurance)) +
  geom_bar(stat="identity") +
  xlab("school") + 
  ggtitle("school reputation")
p2
```

From the graph we observed that analytic school has high frequency in other school's corpus. German idealism, which Kant belongs to, surprisingly was the least mentioned school (actually, 0 time appeared in other corpus).


## Topic Modeling

```{r}
#create DTM
dtm <- CreateDtm(philosophy_data$tokenized_txt, 
                 doc_names = philosophy_data$author, 
                 ngram_window = c(1, 2))
#explore the basic frequency
tf <- TermDocFreq(dtm = dtm)
original_tf <- tf %>% select(term, term_freq,doc_freq)
rownames(original_tf) <- 1:nrow(original_tf)
# Eliminate words appearing less than 2 times or in more than half of the
# documents
vocabulary <- stf$term[ tf$term_freq > 1 & tf$doc_freq < nrow(dtm) / 2 ]
dtm = dtm

```






## Conclusion



